\documentclass[12pt]{article}
\input{Misc/definiciones}
%

%	Margins, etc.
%-----------------------------------------
%
\renewcommand {\baselinestretch} {1}

\setlength{\hoffset}       {0.0mm}
\setlength{\oddsidemargin} {0.0mm} % Margins is 1" + \hoffset + \oddsidemargin
\setlength{\evensidemargin}{0.0mm} % Margins is 1" + \hoffset + \evensidemargin
\setlength{\marginparwidth}{0.0mm} % for Margin Notes
\setlength{\marginparsep}  {0.0mm} % separation between Margin Notes and Body

\setlength{\voffset}       {-12.5mm}
\setlength{\topmargin}     {2.5mm} % Margins is 1" + \voffset + \topmargin (Header starts)
\setlength{\headheight}    {4.5mm} % Header height (after 1" + \voffset + \topmargin)
\setlength{\headsep}       {7.5mm} % separation between header and Body
\setlength{\topskip}       {2.5mm} % separation to first line of text.

\setlength{\textheight}    {210.0mm} % Body Height %{8.625truein}%{219.075mm}
 		% After 1" + \voffset + \topmargin + \headheight + \headsep

\setlength{\textwidth}     {159.0mm} % Body Width %{6.255truein}%{158.877mm}
 		% After 1" + \hoffset + \sidemargin + \marginparsep + \marginparwidth

\setlength{\footskip}      {7.5mm} % separation between Body and Footer (bottom)

\def\newVolume#1{
 	\pagenumbering{arabic}
	\setcounter{page}{0}
}
%
%	------- Title -------
%
\author{
    Benito R. Fern\'andez, Ph.D.
    \texttt{[benito@utexas.edu]}\\
    Juan Rincon \texttt{[jrincon@utexas.edu]}
    }
\title{\huge{Hybrid eXtreme Computer \cool{HxC}}\\
Hardware Accelerator\\
for Machine Learning}
\date{September 12, 2017}


%
%	------- Begin Document -------
%
\begin{document}
	\maketitle
	\vspace{10.0mm}
	\centerline{\huge\textbf{\cool{W H I T E    P A P E R}}}
    \vspace{5.0mm}
    \centerline{\LARGE\textbf{\color{red}\cool{[ P R O P R I E T A R Y ]}}}
    \clearpage
	\vspace{10mm} 
    \centerline{\Large\textbf{\cool{SUMMARY}}}
    \vspace{2mm}\hrule
        Artificial Intelligence (\cool{AI}) has become popular in the past five years. Several industries have realized that capabilities such as pattern recognition and forecast, can help their applications to be more robust and efficient.  Artificial Intelligence has remained the same since the late 90's. Neural networks have different architectures such as multi layer feed-forward, and activation functions such as a simple hyperbolic tangent. There are training and learning strategies. Depending on the training strategies a computer can behave intelligent or not. However, if the neural network is complex with several layers and nodes, the algorithm can take several hours or days to train. Some of the state of the art accelerators are software base. They focus on how to make the training algorithm more efficient. Other state of the art accelerators are based on Graphics Processing Units (GPU). GPUs are specialize silicone that are optimize for linear algebra usually used to create real-time graphics. Because of its fast linear algebra capabilities it can train networks between 3 to 7 times faster if only the Central Processing Units (CPU) is used. However, as neural network become more complex, GPUs and software accelerators become obsolete and hours of computational time turn into an extensive task. Researchers at The University of Texas at Austin have developed a technology named (\cool{HxC}), a cutting-edge architecture based on Field Programmable Arrays. 
    \par
	\vspace{10mm} 
    \centerline{\Large\textbf{\cool{INTELLECTUAL MERIT}}}
    \vspace{2mm}\hrule
        The \cool{HxC} architecture uses an asynchronous silicone to invert matrices and optimized circuitry to perform basic lineal operations. Hence creating fast and reliable training solutions. Computations will be unconditionally stable, and without truncation and rounding errors.
    \par        
	\vspace{10mm} 
    \centerline{\Large\textbf{\cool{BROADER IMPACTS}}}
    \vspace{2mm}\hrule
    For the final product we envision a PCIe board that can be attached to any computer. A user-friendly AP similar to Basic Linear Algebra Subprograms (BLAS) libraries available for different programming languages. Additionally, a service model can be used where companies and costumers can use our server farms with our hardware to train the networks.
    
    \cool{AI} is a growing market and it is predicted to surprise a market value of \$60 billion dollars by 2025. {\color{rojo}Referece}
    
    \clearpage
    
     \centerline{\Large\textbf{{The Hybrid Computer}}:
                               {A Paradigm Shift}}\
     \vspace{-7.5mm}\hrule\vspace{-2.5mm}
    % (The Heilmeier Catechism)
    %---------------------------------------------
    % When George Heilmeier was the director of DARPA (then called ARPA) in the mid-1970s, he expected every proposal for a new research program to answer a standard set of questions. These questions have been called the Heilmeier Catechism or Heilmeier's criteria. Known by many technology managers, his questions helped ensure a technical idea had practical application.
    %Heilmeier's criteria are a useful way to test your own group's vision and as a way to convey to others what you hope to accomplish. Several versions have circulated since, and the most common version is as follows:
    
    \begin{enumerate}\large
        \item[\UUno]     
            \textbf{What is the problem and why is it hard?} \par
            
            %(articulate your objectives using absolutely no jargon)}
            Complex Artificial neural networks require lots of computational time and resources to training. 
            \par
        \item[\DDos]     
            \textbf{How is it done today, and what are the limits of current practice?} \par
            
            Algorithms can be train using GPUs. The supercomputers needed to do this on a large scale are 
            very expensive and consume a lot of power.
            \par
        \item[\TTres]    
            \textbf{What's new in your approach, 
            and why do you think it will be successful? 
            What gives evidence that it will work?} \par
            
            Our solution, a hybrid computer, requires no such approximation. Instead 
            it creates a simulacrum of the system directly in an analog circuit
            controlled by a digital counterpart, which requires much less switching. 
            Thus a hybrid computer combines the best
            of both analog and digital computers without the drawbacks of either.
            Simulations and PCBs (Printed Circuit Boards) prototypes have 
            demonstrated these mixed-signal circuits.
            \par
        \item[\CCuatro]  
            \textbf{Who cares? 
            If you're successful, what difference will it make?} \par
            
            The archetypes are people and organizations that require extremely fast 
            computations to solve STEM problems at a fraction of supercomputers' 
            cost and power consumption.
            If successful, we will have supercomputer performance on a desktop
            size and have created a new computer paradigm.
            \par
        \item[\CCinco]   
            \textbf{What are the risks and the payoffs?} \par
            
            The risk is that the technology is not as fast and accurate as
            expected because of fabrication methods. 
            The benefit is 1,000 times current supercomputer speeds 
            at a fraction of their cost.
            The result is a computer that could solve problems at speeds between 
            supercomputers and quantum computers.
             \par
        \item[\SSeis]    
            \textbf{How much will it cost? How long will it take?} \par
            We anticipate in the long run, the project will cost about \$10M
            and it will take close to 6 years.
            The initial development may cost \$5M and it will take about to 4 
            years.
            In order to validate a discrete components solution will require 
            \$1M and 18 months.
            \par
        \item[\SSiete]   
            \textbf{What are the midterm and final ``exams'' to 
            check for success?}\par
            
            For the validation: demonstrate Pareto improvements in speed and accuracy   
            over the digital alternative.
            For the initial development: show further improvement of IC implementation.
            For the long run: apply tool to complex problems in representative 
            application areas.
    \end{enumerate}

\end{document}